---
title: "Snakes and Ladders"
author: "Suraj Nath"
date: "Feb. 19, 2017"
output:
  pdf_document: default
  html_document: default
---
# Snakes and Ladders Game Simulation with R

## Introduction

Snakes and Ladders is a very simple board game between two or more players. The game has numbered squares that the player moves through by rolling a 6 sided dice but if a player lands on a certain square they get moved up (ladder) or down (snakes). This continues on until the a player reaches the last numbered square.

---

The ladders and slides/snakes will be set up as a data frame,

```{r}
ladder.df <- data.frame(start=c(1,4,9,21,28,36,51,71,80), end=c(38,14,31,42,84,44,67,91,100))
slide.df <- data.frame(start=c(98,95,93,87,64,62,56,49,47,16), end=c(78,75,73,24,60,19,53,11,26,6))
```

``` {r}
library(knitr)
```

The ladders:

``` {r}
kable(ladder.df, align="c")
```

The Snakes:

``` {r}
kable(slide.df, align="c")
```

```{r}
curLoc <- 0 # Current location
nroll <- 0 # Number of rolls
slides <- 0 # Number of slides encountered
ladders <- 0 # Number of ladders encountered
# Keep rolling dice and moving until reach 100 or greater ending the game
while(curLoc < 100) {
  roll <- sample(6,1) # generate random number between [1 to 6]
  curLoc <- curLoc + roll # increase position
  nroll <- nroll + 1 # increase number of rolls
  # Need to check if we landed on a ladder or slide and move forward or back
  if (any(ladder.df$s %in% curLoc)) {
    curLoc <- ladder.df$e[ladder.df$s %in% curLoc]
    ladders <- ladders + 1
  }
  if (any(slide.df$s %in% curLoc)) {
    curLoc <- slide.df$e[slide.df$s %in% curLoc]
    slides <- slides + 1
  }
}
```

``` {r}
library(foreach)
library(doParallel)
```

``` {r}
registerDoParallel(cores=4)
```

``` {r}
getDoParWorkers()
```
``` {r}
num.iter <- 500 # Number of play throughs

# Get timing as well
stime <- system.time({
  out.seq <- foreach(icount(num.iter), .combine=rbind) %do% {
    curLoc <- 0
    nroll <- 0
    slides <- 0
    ladders <- 0
    # Keep rolling dice and moving until reach 100 or greater ending the game
    while(curLoc < 100) {
      roll <- sample(6,1) # generate random number between [1 to 6]
      curLoc <- curLoc + roll # increase position
      nroll <- nroll + 1 # increase number of rolls
      # Need to check if we landed on a ladder or slide and move forward or back
      if (any(ladder.df$s %in% curLoc)) {
        curLoc <- ladder.df$e[ladder.df$s %in% curLoc]
        ladders <- ladders + 1
      }
      if (any(slide.df$s %in% curLoc)) {
        curLoc <- slide.df$e[slide.df$s %in% curLoc]
        slides <- slides + 1
      }
    }
    # Create output to store, num rolls, num ladders hit, num slides hit
    out.info <- c(nroll, ladders, slides)
  }})[3]
```
Time taken by simulation

```{r}
stime
```

Take a look at a histogram of number of rolls to complete the game

``` {r }
h <- hist(out.seq[,1], breaks=seq(0,305,5))
```

``` {r}
plot(h, main="", xlab="Number of Rolls", ylab="Games Completed", xlim=c(0,200), axes=F)
axis(1, at=seq(0,200,5))
axis(2)
```

Plot for percentage chance to win the game in n rolls:

``` {r}
d <- density(out.seq[,1])
d$y <- d$y * 100
plot(d, main="Percentage Chance to Win in n-Rolls", xlab="Number of Rolls", ylab="Percentage", xlim=c(0,200), axes=F)
axis(2)
axis(1, at=seq(0,200,5))
abline(v=d$x[which.max(d$y)], col="red")
```

cumulative distribution function:

``` {r}
plot(ecdf(out.seq[,1]), xlab="Number of Rolls", ylab="",main="")
```