---
title: "Snakes and Ladders"
author: "Suraj Nath"
date: "Feb. 19, 2017"
output:
  pdf_document: default
---
# Snakes and Ladders Game Simulation with R

## Introduction

Snakes and Ladders is a very simple board game between two or more players. The game has numbered squares that the player moves through by rolling a 6 sided dice but if a player lands on a certain square they get moved up (ladder) or down (snakes). This continues on until the a player reaches the last numbered square.

---

The ladders and slides/snakes will be set up as a data frame,

```{r}
ladder.df <- data.frame(start=c(3,11), end=c(13,17))
slide.df <- data.frame(start=c(10,16,18), end=c(5,2,8))
```

``` {r}
library(knitr)
```

The ladders:

``` {r}
kable(ladder.df, align="c")
```

The Snakes:

``` {r}
kable(slide.df, align="c")
```


``` {r}
library(foreach)
library(doParallel)
```

``` {r}
registerDoParallel(cores=4)
```

``` {r}
getDoParWorkers()
```
``` {r}
num.iter <- 100 # Number of play throughs aka games

# Get timing as well
stime <- system.time({
  out.seq <- foreach(icount(num.iter), .combine=rbind) %do% {
    curLoc <- 0
    nroll <- 0
    slides <- 0
    ladders <- 0
    # Keep rolling dice and moving until reach 17 or greater ending the game
    while(curLoc < 17) {
      roll <- sample(6,1) # generate random number between [1 to 6]
      curLoc <- curLoc + roll # increase position
      nroll <- nroll + 1 # increase number of rolls
      # Need to check if we landed on a ladder or slide and move forward or back
      if (any(ladder.df$start %in% curLoc)) {
        curLoc <- ladder.df$end[ladder.df$start %in% curLoc]
        ladders <- ladders + 1
      }
      if (any(slide.df$start %in% curLoc)) {
        curLoc <- slide.df$end[slide.df$start %in% curLoc]
        slides <- slides + 1
      }
    }
    # Create output to store, num rolls, num ladders hit, num slides hit
    out.info <- c(nroll, ladders, slides)
  }})[3]
```
####Time taken by simulation

```{r}
stime
```

Plot for percentage chance to win the game in n rolls:

``` {r}
d <- density(out.seq[,1])
d$y <- d$y * 100
plot(d, main="Percentage Chance to Win in n-Rolls", xlab="Number of Rolls", ylab="Percentage", xlim=c(0,200), axes=F)
axis(2)
axis(1, at=seq(0,200,5))
abline(v=d$x[which.max(d$y)], col="red")
```

cumulative distribution function:

``` {r}
plot(ecdf(out.seq[,1]), xlab="Number of Rolls", ylab="",main="")
```